\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-19 notes/2loopNLSM.tex
some more edits
Added some graphs for two-loop construction. Absorbed helicity decomposition games into the beginning of section 3. Restructed some games wiith semi-YM. Eyes are bleeding now though, so going to add more more citatiios ad thenn hand off

With this solver, we are able to compute a two-loop integrand for NLSM that globally manifests the duality off-shell. This represents a new benchmark for color-dual representations in non-supersymmetric gauge theories. However in contrast, we find surprisingly that Yang-Mills does not permit a globally color-dual representation, even when considering the most general polynomial ansatz of Lorentz covariant kinematics. Concretely, we find a sharp failure point between the ``bowtie'' cut, and the following jacobi triple:
\begin{equation}
   \NMCutC
  \Rightarrow
  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
\end{equation}
We comment on the implications of this finding in \cref{conclusions}, and discuss alternative approaches where one must relax field theoretic locality in order to accommodate the construction of globally color-dual multi-loop integrands.

@@

As one can see above, the Jacobi identity of \ref{cubicJac} fails only in terms with two factors of polarization dot products, $(\varepsilon\varepsilon)^2$. Whereas, if we restricted ourselves to just considering factors with a single polarization dot product, the Jacobi identity of Yang-Mills would be satisfied \textit{off-shell} and in arbitrary spacetime dimensions:
\be
{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4\big|^{(\varepsilon\varepsilon)^1}+\text{cyc}(234) =0
\ee
Thus for our approach at one-loop, we aim to build color-dual integrands directly from kinematic factors of this form. The organizational principle underlying this construction can be easily understood in terms of a polarization decomposition of vector amplitudes introduced by one of the authors \cite{Pavao:2022kog}, which we summarize briefly below. 
\subsection{Block Decomposition of Yang-Mills}
The $D$-dimensional Lagrangians of \ref{} can be understood as selecting specific on shell states to isolate the cubic sector of Yang-Mills at a given loop order. Start with reducible amplitude block decomp from Ref. \cite{Pavao:2022kog}:
\begin{equation}\label{eq:pureVecRABD}
A_{(\sigma)}^{\text{YM}} = \sum_{k=0}^{\lfloor |\sigma|/2\rfloor}\sum_{\rho \in S^{2|k}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\end{equation}
By a simple mass-dimensioin argument, we know the tree-level cubic sector must be at $\mathcal{O}((\varepsilon\varepsilon)^1)$:
\be
A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\ee
while at one-loop, the cubic sector corresponds to $\mathcal{O}((\varepsilon\varepsilon)^0)$ in polarization dot products:
\be
A_{(\text{1-loop})}^{\text{cubic}} = \sum_{\rho \in S^{2|0}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\ee
When decomposed in this way, in order for the full amplitude to be gauge invariant, the polarization stripped building blocks, must obey a set of Ward-Identities between different helicity sectors:
 \begin{equation}\label{eq:GIrelA}
\Delta_{(\sigma)}^{(\rho)}\Big|_{\epsilon_i\rightarrow k_i} =-
\sum_{j \in \rho^c} (k_i \varepsilon_j)\Delta_{(\sigma )}^{(\rho\cup (ij))} \,.
\end{equation}
With this in hand, we can construct a Lagrangian description of the of the cubic sector for Yang-Mills, and will demonstrate that the resulting amplitudes with manifestly color-dual Feynman rules are equivalent to both SDYM and NLSM through one-loop. 
\subsection{Semi-abelian Yang-Mills theory}\label{semiYM}
As we demonstrate above, if we include factors of $(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to keep the Yang-Mills four-point contact for color-kinematics duality to be restored on-shell. However, the contrapositive is also true -- if we get rid of the four-point Yang-Mills vertex, then we only need terms that contribute to the manifestly color-dual cubic sector of the theory.

We can achieve this construction by splitting the gauge group of the full Yang-Mills action from $G \rightarrow G_L \times G_R$, where the full non-abelian gauge symmetry is restored only when we identify $G_L = G_R$. However, if we break the left gauge group down to $G_L \rightarrow U(1)^{N^2}$, and take the right gauge group to $G_R \rightarrow U(N)$, then we are left with a semi-abelian theory that is gauge invariant in the preffered $U(1)$-directions. We call this manifestly color-dual theory, \textit{semi-abelian Yang-Mills},
\begin{eBox}
\be
\label{eq:semiYM}
\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
\ee
\end{eBox}
where,
\be
\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
\ee
\be
F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c .
\ee
Here we can think of the abelian vector as a background field that sources on-shell $A_\mu$ currents. Indeed, as we describe in the Appendix \ref{}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{}, J-theory \cite{}, and self-dual Yang-Mills \cite{}.
Specifically, semi-Abelian YM is simply a clever reinterpretation of the Lagrangian obtained by integrating an auxiliary field into the J-theory equations of motion.
We can use the Ward identity of \ref{eq:GIrelA} to check that the amplitudes are indeed gauge invariant with the abelian polarizations are taken on-shell, $\bar{\varepsilon} \rightarrow k$.

@@

\subsection{One-loop color-dual integrands}\label{oneLoopCK}
Our first application of this theory for color-dual construction at loop level is for self-dual Yang-Mills (SDYM). At tree-level, the off-shell cubic vertices can be written in terms of light cone coordinates \cite{}:
\be
X(p,k) = p_u k_w-p_w k_u
\ee
At loop-level, this construction needs to be analytically continued to general dimension in order to apply dimensional regularization at one-loop. This can be done using the cubic semi-YM vertices of the previous section:
\be
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\varepsilon_3)(\varepsilon_2 k_3) -  (\varepsilon_2\varepsilon_3)(\varepsilon_1 k_3)
\ee
Plugging in on-shell all-plus helicity states in light-cone gauge will yield precisely the 4D SDYM vertex, up to an unphysical phase. Of course, this has the advantage of permitting a $D$-dimensional construction of the one-loop integrand. Below we provide a four-point example:
\be
\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\mathcal{X}(k_3,l_3)\mathcal{X}(k_4,l_4)\rangle
\ee
where $l_i = l+k_1+k_2+\cdots+ k_i$. In general, the $n$-gon vertex would be
\be
\mathcal{N}^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\cdots \mathcal{X}(k_n,l_n) \rangle
\ee
Due to the state-sum of internal loop factors, $\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}=D$, the integrand above depends explicitly on the spacetime dimension, $D$. By taking a derivative\footnote{Another way to understand this derivative is that it selects the large $D$ behavior of the integrand.}, we can recover the integrand needed for all-plus one-loop amplitudes with an internal scalar:
\be
\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 k_1)(l_2 k_2)\cdots (l_n k_n)
\ee
This integrand numerator with internal scalar loop is precisely what one would obtain from the Feynman rules of YZ-theory, absent the $XZ$ internal vector loop. For more background, we refer the reader to appendix \ref{}. 
\be
 \mathcal{N}^{\text{NLSM}}_{n\text{-gon}}=\left[\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
\ee
Where we have define the antisymmetric kinematic variable, $[LR] = l_L^2 - l_R^2$
\subsection{Two-loop obstruction}\label{2LoopObstruction}
At two-loop, introducing terms that conspire with four-point contacts is unavoidable (add diagram). Thus, to approach the problem of two-loop construction, we employ an ansatz based approach. 
\section{Two-loop bootstrap}\label{2loopBoot}
We now employ the color-dual bootstrap method described in \cref{bootstrap}. We will employ an ansatz constructed from  $D$-dimensionally Lorentz covariant kinematics. To fix remaining freedom in the NLSM bootstrap, we will match down to ZM theory in $D=2$. This is merely an aesthetic choice, so the final results of both the NLSM and Yang-Mills bootstraps are dimensionally agnostic.
\subsection{Two-loop NLSM}\label{2loopNLSM}
\label{sec:pions}

@@

\paragraph{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
\be
\mathcal{L}^{\text{YM}} = -\frac{1}{4}F_{\mu\nu}F^{\mu\nu}
\ee
To obtain the Lagrangian for self-dual Yang-Mills, we applyy the self-dual condition that equates the field strength to its dual 2-form:
\be\label{SDcon}
F_{\mu\nu} = \frac{1}{2} \varepsilon_{\mu\nu\rho\sigma}F^{\rho\sigma}
\ee
where $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu ,A_\nu]$ is the non-abelian $SU(N)$ field strength. Solutions to the self-dual condition automatically satisfy the Yang-Mills equation of motion due to the Bianchi identity:
\be
D^\mu F^{\mu\nu} = \frac{1}{2} \varepsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0
\ee
Solutions to \cref{SDcon} correspond to instanton configurations that are probed by the gauge field path integral in the full non-perturbative description of Yang-Mills. In this paper, we will focus on the perturbative aspects of this constraint. Transforming from Cartesian coordinates to light cone coordinantes, $(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, which take the following definition:
\be
u = t+x,\quad v=t-x, \quad w = y+iz
\ee
which gives the following expression for the invariant line element:
\be
ds^2 = 2(dudv - dwd\bar{w}) = dt^2 - d\vec{x}\cdot d\vec{x}
\ee
Applying this coordinate transformation to the self-dual condition of \cref{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
\begin{align} \label{SDLightCone1}
F_{uw} &=0\,,
\\
 \label{SDLightCone2}
 F_{uv} &= F_{w\bar{w}}\,,
\\
 \label{SDLightCone3}
 F_{v\bar{w}} &= 0\,,
\end{align}
Thus, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the self-dual condition:
\be
A_u=0 \text{ and } (\ref{SDLightCone1}) \quad\Rightarrow \quad A_w=0
\ee
The \cref{SDLightCone2} then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom
\be
A_w=0\,,\,A_u=0 \text{ and } (\ref{SDLightCone2}) \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
\ee
This constraint is  satisfied with the following definition of the gauge field in terms of a single scalar degree of freedom which we call $\Psi$:
\be\label{SDDef}
A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi,
\ee
Using this definition on the final \jm{first?} self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
\be\label{SDEOM}
(\ref{SDLightCone1}) \text{ and } (\ref{SDDef}) \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
\ee
Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange multiplier, we obtain the following interaction Lagrangian for self-dual Yang-Mills theory:
\be
\mathcal{L}^{\text{SDYM}} = (\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ]
\ee
The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
\be
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
\ee
In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}. In this form, we can see the effect \cref{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex. Before proceeding, it is important to note that the mass-dimension of the theory appears to differ from that of Yang-Mills -- we comment on this in detail in our appendix on spinor-helicity variables and conventions.

@@

This theory is one-to-one with the observables amplitudes of YZ-theory when only considering $Z-\bar{Z}$ on-shell states. As such, the single vertex in this theory is the same as for YZ theory: 
\be
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
\ee

>>>>

With this solver, we are able to compute a two-loop integrand for NLSM that globally manifests the duality off-shell. This represents a new benchmark for color-dual representations in non-supersymmetric gauge theories. However in contrast, we find surprisingly that Yang-Mills does not permit a globally color-dual representation, even when considering the most general polynomial ansatz of Lorentz covariant kinematics. Concretely, we find a sharp failure point between the ``bowtie'' cut, and the following jacobi triple:
\begin{eBox}
\begin{equation}
   \NMCutC
  \Rightarrow
  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
\end{equation}
\end{eBox}
We comment on the implications of this finding in \cref{conclusions}, and discuss alternative approaches where one must relax field theoretic locality in order to accommodate the construction of globally color-dual multi-loop integrands.

@@

As one can see above, the Jacobi identity of \ref{cubicJac} fails only in terms with two factors of polarization dot products, $(\varepsilon\varepsilon)^2$. Whereas, if we restricted ourselves to just considering factors with a single polarization dot product, the Jacobi identity of Yang-Mills would be satisfied \textit{off-shell} and in arbitrary spacetime dimensions:
\be
{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4\big|^{(\varepsilon\varepsilon)^1}+\text{cyc}(234) =0
\ee
Thus for our approach at one-loop, we aim to build color-dual integrands directly from kinematic factors of this form. The organizational principle underlying this construction can be easily understood in terms of a polarization decomposition of vector amplitudes introduced by one of the authors \cite{Pavao:2022kog}, 
\begin{equation}\label{eq:pureVecRABD}
A_{(\sigma)}^{\text{YM}} = \sum_{k=0}^{\lfloor |\sigma|/2\rfloor}\sum_{\rho \in S^{2|k}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\end{equation}
By a simple mass-dimensioin argument, we know the tree-level cubic sector of Yang-Mills must be at $\mathcal{O}((\varepsilon\varepsilon)^1)$:
\be
A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\ee
while at one-loop, the cubic sector corresponds to $\mathcal{O}((\varepsilon\varepsilon)^0)$ in polarization dot products:
\be
A_{(\text{1-loop})}^{\text{cubic}} = \sum_{\rho \in S^{2|0}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\ee
When decomposed in this way, the polarization stripped building blocks must obey a set of Ward-Identities between different helicity sectors in order for the full amplitude to be gauge invariant,:
 \begin{equation}\label{eq:GIrelA}
\Delta_{(\sigma)}^{(\rho)}\Big|_{\epsilon_i\rightarrow k_i} =-
\sum_{j \in \rho^c} (k_i \varepsilon_j)\Delta_{(\sigma )}^{(\rho\cup (ij))} \,.
\end{equation}
With this in hand, we can construct a Lagrangian description of the of the cubic sector for Yang-Mills, and will demonstrate that the resulting amplitudes with manifestly color-dual Feynman rules are equivalent to both SDYM and NLSM through one-loop. 
\subsection{Semi-abelian Yang-Mills theory}\label{semiYM}
As we demonstrate above, if we include factors of $(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to keep the Yang-Mills four-point contact for color-kinematics duality to be restored on-shell. However, the contrapositive is also true -- if we get rid of the four-point Yang-Mills vertex, then we only need terms that contribute to the manifestly color-dual cubic sector of the theory.

We can achieve this construction by splitting the gauge group of the full Yang-Mills action from $G \rightarrow G_L \times G_R$, where the full non-abelian gauge symmetry is restored only when we identify $G_L = G_R$. However, if we break the left gauge group down to $G_L \rightarrow U(1)^{N^2}$, and take the right gauge group to $G_R \rightarrow U(N)$, then we are left with a semi-abelian theory that is gauge invariant in the preffered $U(1)$-directions. We call this manifestly color-dual theory, \textit{semi-abelian Yang-Mills},
\begin{eBox}
\be
\label{eq:semiYM}
\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
\ee
\end{eBox}
where,
\be
\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
\ee
\be
F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c .
\ee
Here we can think of the abelian vector as a background field that sources on-shell $A_\mu$ currents. Indeed, as we describe in the Appendix \ref{}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{}, J-theory \cite{}, and self-dual Yang-Mills \cite{}. The Feynman rules fo this theory are simply:
\be
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
\ee
Specifically, semi-Abelian YM is simply a clever reinterpretation of the Lagrangian obtained by integrating an auxiliary field into the J-theory equations of motion.
We can use the Ward identity of \ref{eq:GIrelA} to check that the amplitudes are indeed gauge invariant with the abelian polarizations are taken on-shell, $\bar{\varepsilon} \rightarrow k$.

@@

\subsection{One-loop color-dual integrands}\label{oneLoopCK}
Our first application of this theory for color-dual construction at loop level is for self-dual Yang-Mills (SDYM). At tree-level, the off-shell cubic vertices can be written in terms of light cone coordinates \cite{}:
X(p,k) = p_u k_w-p_w k_u
At loop-level, this construction needs to be analytically continued to general dimension in order to apply dimensional regularization at one-loop. This can be done using the cubic semi-YM vertices of the previous section:
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\varepsilon_3)(\varepsilon_2 k_3) -  (\varepsilon_2\varepsilon_3)(\varepsilon_1 k_3)
Plugging in on-shell all-plus helicity states in light-cone gauge will yield precisely the 4D SDYM vertex, up to an unphysical phase. Of course, this has the advantage of permitting a $D$-dimensional construction of the one-loop integrand. Below we provide a four-point example:
\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\mathcal{X}(k_3,l_3)\mathcal{X}(k_4,l_4)\rangle
where $l_i = l+k_1+k_2+\cdots+ k_i$. In general, the $n$-gon vertex would be
\mathcal{N}^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\cdots \mathcal{X}(k_n,l_n) \rangle
Due to the state-sum of internal loop factors, $\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}=D$, the integrand above depends explicitly on the spacetime dimension, $D$. By taking a derivative\footnote{Another way to understand this derivative is that it selects the large $D$ behavior of the integrand.}, we can recover the integrand needed for all-plus one-loop amplitudes with an internal scalar:
\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 k_1)(l_2 k_2)\cdots (l_n k_n)
This integrand numerator with internal scalar loop is precisely what one would obtain from the Feynman rules of YZ-theory, absent the $XZ$ internal vector loop. For more background, we refer the reader to appendix \ref{}. 
 \mathcal{N}^{\text{NLSM}}_{n\text{-gon}}=\left[\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
Where we have define the antisymmetric kinematic variable, $[LR] = l_L^2 - l_R^2$
\subsection{Two-loop obstruction}\label{2LoopObstruction}
At two-loop, introducing terms that conspire with four-point contacts is unavoidable. At one-loop, we were able to avoid internal contractions of $\bar{A}_\mu A^\mu$ by selecting external states of appropriate weight. However, at two-loop when choosing all external $A_\mu$ states, the amplitude vanishes in semi-YM theory:
\mathcal{A}^{\text{semi-YM}}_{\text{2-loop}}(+,+,+,+)=0
In order to produce non-vanishing interactions, we would need to reintroduce $D$-dimensional vertices from the diagonal group of $G_L\times G_R$. Doing so will necessarily introduce internal contractions of $\bar{A}_\mu A^\mu$,
\mathcal{A}^{\text{YM}}_{\text{2-loop}}(+,+,+,+)=\doubleBoxObstructionA +\doubleBoxObstructionB+\cdots 
However, this immediately runs into the difficulty of introducing the four-point contact needed for color-kinematics to be satisfied on all internal edges. To do this prescriptively would require knowledge of the full kinematic algebra for Yang-Mills off-shell. Since this is presently unavailable, to approach the problem of two-loop construction, we instead employ an ansatz based approach. 
\section{Two-loop bootstrap}\label{2loopBoot}
We now employ the color-dual bootstrap method described in \cref{bootstrap}. We will employ an ansatz constructed from  $D$-dimensionally Lorentz covariant kinematics. To fix remaining freedom in the NLSM bootstrap, we will match down to ZM theory in $D=2$. This is merely an aesthetic choice, so the final results of both the NLSM and Yang-Mills bootstraps are dimensionally agnostic.
\subsection{Two-loop NLSM}\label{2loopNLSM}
\label{sec:pions}

@@

\paragraph{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
\be
\mathcal{L}^{\text{YM}} = -\frac{1}{4}F_{\mu\nu}F^{\mu\nu}
\ee
To obtain the Lagrangian for self-dual Yang-Mills, we applyy the self-dual condition that equates the field strength to its dual 2-form:
\be\label{SDcon}
F_{\mu\nu} = \frac{1}{2} \varepsilon_{\mu\nu\rho\sigma}F^{\rho\sigma}
\ee
where $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu ,A_\nu]$ is the non-abelian $SU(N)$ field strength. Solutions to the self-dual condition automatically satisfy the Yang-Mills equation of motion due to the Bianchi identity:
\be
D^\mu F^{\mu\nu} = \frac{1}{2} \varepsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0
\ee
Solutions to \cref{SDcon} correspond to instanton configurations that are probed by the gauge field path integral in the full non-perturbative description of Yang-Mills. In this paper, we will focus on the perturbative aspects of this constraint. Transforming from Cartesian coordinates to light cone coordinantes, $(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, which take the following definition:
\be
u = t+x,\quad v=t-x, \quad w = y+iz
\ee
which gives the following expression for the invariant line element:
\be
ds^2 = 2(dudv - dwd\bar{w}) = dt^2 - d\vec{x}\cdot d\vec{x}
\ee
Applying this coordinate transformation to the self-dual condition of \cref{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
\begin{align} \label{SDLightCone1}
F_{uw} &=0\,,
\\
 \label{SDLightCone2}
 F_{uv} &= F_{w\bar{w}}\,,
\\
 \label{SDLightCone3}
 F_{v\bar{w}} &= 0\,,
\end{align}
Thus, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the self-dual condition:
\be
A_u=0 \text{ and } (\ref{SDLightCone1}) \quad\Rightarrow \quad A_w=0
\ee
The \cref{SDLightCone2} then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom
\be
A_w=0\,,\,A_u=0 \text{ and } (\ref{SDLightCone2}) \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
\ee
This constraint is  satisfied with the following definition of the gauge field in terms of a single scalar degree of freedom which we call $\Psi$:
\be\label{SDDef}
A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi,
\ee
Using this definition on the first self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
\be\label{SDEOM}
(\ref{SDLightCone1}) \text{ and } (\ref{SDDef}) \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
\ee
Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange multiplier, we obtain the following interaction Lagrangian for self-dual Yang-Mills theory:
\be
\mathcal{L}^{\text{SDYM}} = (\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ]
\ee
The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
\be
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
\ee
In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}. We can see the effect \cref{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex. Before proceeding, it is important to note that the mass-dimension of the theory appears to differ from that of Yang-Mills -- we comment on this in detail in our appendix on spinor-helicity variables and conventions.

@@

This theory is one-to-one with the observables amplitudes of YZ-theory when only considering $Z$-$\bar{Z}$ on-shell states. As such, the single vertex in this theory is the same as the pure vector vertex of YZ theory in Lorenz gauge, where $\partial_\mu J^\mu = 0$: 
\be
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
\ee
